\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
correct wrong word: user >use

We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after user. We recruited five participants per experimental condition to gather qualitative data; this is considered the optimal number of measurements to maximize the cost-benefit ratio~\cite{howmanyusers}. We performed our quantitative experiments at a behavioral laboratory many participants at a time, using instrumentation to capture evaluation metrics. We recruited twenty users per experimental condition to gather quantitative data; this is considered to be the minimum for yielding statistically significant measurements~\cite{howmanyusers}.

>>>>

We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after use. We recruited five participants per experimental condition to gather qualitative data; this is considered the optimal number of measurements to maximize the cost-benefit ratio~\cite{howmanyusers}. We performed our quantitative experiments at a behavioral laboratory many participants at a time, using instrumentation to capture evaluation metrics. We recruited twenty users per experimental condition to gather quantitative data; this is considered to be the minimum for yielding statistically significant measurements~\cite{howmanyusers}.
